Clouds and Sensitivities Across a Hierarchy of GFDL CMIP6 Models

### 2020-11-03 Silvers_cfmip.tex
rename Silvers_cfmip_CRE_SinglePanel.tex -> Silvers_cfmip_CRE_3Pan_SingleFig.tex and include minor changes to Silvers_cfmip.tex

@@

Before discussing the climate sensitivities of AM4/CM4 and how they are influenced by cloud feedbacks we assess
the clouds and radiative fluxes which are simulated by AM4.0 over the recent period of 1979-2014.  This is done 
by comparing satellite based observations to the \textit{amip} experiment that is part of GFDLs 
contribution to CMIP6.  
During the development and documentation of AM4.0 \cite{Zhao_etal_2018a, Zhao_etal_2018b}, 
(Z18a and Z18b hereafter) 
and CM4 \cite{Held_etal_2019}, specific cloud properties such as the 
cloud droplet number, cloud fraction, and the partition of cloud water into liquid or ice were noted, but 
accurately modeling the radiative fluxes at the top of the atmosphere was determined to be a 
higher priority partly because of the large observational uncertainties of those cloud properties (Z18a,b).   
Based on the initial analysis for those papers, the cloud properties of AM4.0 were determined to be
at least as consistent with observations as previous generations of GFDL models.  Z18a also noted 
that AM4.0 underestimates the liquid droplet number over oceans and downwind of the aerosol emission 
sources.   
Comparisons of AM4.0 with observations from ISCCP and MODIS in Z18a (their Figure 10) showed an underestimate of 
the optically thin low clouds and the mid-level clouds.  
However, the observational uncertainty for some of these properties prohibited firm conclusions.  This paper
uses additional observations and a more thorough analysis of the clouds in AM4/CM4 to better determine 
the quality of the cloud simulations.        
In this section we first compare the simulated and observed cloud fraction.  We then compare  
the simulated TOA radiative fluxes from AM4.0 to those observed by CERES.

@@

@@

During the developmental of the AM4.0 GFDL model particular care was given to ensuring that the energy budget at 
the top of the atmosphere compared well with observations (Z18a).  The data set that was used as a target
was the CERES-EBAF TOA radiative fluxes, version 2.8 (Loeb et al., 2009).  
% probably don't need the next few sentences but here they are for now...
As a result of this focus AM4.0 succeeded at decreasing several long standing biases from previous GFDL models.  
In particular AM4.0 has a reduced tropical OLR bias and a reduced SW bias over much of the southern hemisphere oceans.   
Based on AM4.0 data that was used for the CMIP6 \textit{amip} experiment, the total TOA flux bias is -0.15 $ \rm{W m^{-2}}$,  % Fig 6 from Z18a
the bias in CRE due to longwave radiative fluxes is $-2.4 \rm{W m^{-2}} $ and the bias due to CRE of the shortwave radiative fluxes   
is $-1.1 \rm{W m^{-2}} $.  
% https://eosweb.larc.nasa.gov/project/ceres/ebaf_toa_table.    % webpage with CERES info
After the AM4.0 development was frozen and the process of documentation 
was underway, the CERES-EBAF data version 4.1 was released.  When comparing the same 
AM4.0 \textit{amip} experiment to the 
newer version of CERES-EBAF data we find biases of $-2.2 \rm{W m^{-2}} $ for the longwave CRE and 
$-2.9 \rm{W m^{-2}} $ for the shortwave CRE (Figure \ref{fig:ceres_cre_4p1}).  Although the magnitude of bias 
differs when compared to the two versions of CERES-EBAF, the spatial pattern is very similar.   
The comparison of the total 
CRE in Figure \ref{fig:ceres_cre_4p1}  shows a cooling of about 25 $\rm{W m^{-2}}$ in AM4.0 which is about 
5 $\rm{W m^{-2}}$ more than CERES-EBAF.  The overall pattern compares
well with the observations although the cooling from the highly reflective stratocumulus regions is too small and
too far from the coastlines. 
This bias is clearly seen in the SW CRE and highlights the regions with the largest
positive CRE bias resulting from too few stratocumulus clouds.  Also of note is a pervasive negative bias in the SH oceans.   
  As previously discussed (e.g. Kay et al., 2012) these longwave and shortwave CRE 
biases are difficult to interpret because model developers often tune models to match particular CERES-EBAF data 
sets despite the well known fact that different versions of the CERES-EBAF data lead to changes in the observed CRE of
several $\rm{W m^{-2}}$.   Our aim in discussing this for AM4.0 is transparency in the model development process, 
as well as to point out that AM4.0 represents a significant improvement in the spatial biases over previous versions
of GFDL models (Z18a) and that both versions of the CERES-EBAF data show similar spatial patterns of bias in the 
simulated clouds  from the AM4.0 \textit{amip} experiment.

@@

The most recent generation of models developed at NOAA's GFDL that have participated in CMIP6 have a large range of climate 
sensitivities (possibly cite Winton et al., Dunne et al.) depending on the experiment of interest and the method used for 
calculation.  One way of quantifying this sensitivity is with the climate feedback parameter, which, for the subset of GFDL models and CMIP6 experiments studied in this paper, varies between -0.46 and -2.1 $\rm{W m^{-2}K^{-1}}$ (Table 1).  
These models (AM4.0 Aquaplanet, AM4.0, CM4.0) simulate several 
distinct geophysical configurations which account for some of the range in values of the climate feedback parameter.  
However, our hypothesis is that the large range of climate sensitivities that are found within this 
group of models is in large part due to variations in the clouds (both their climatology and their feedbacks).

@@

It is also instructive to examine the values of the climate feedback parameters that result from experiments that include a 
dynamic ocean.  Feedbacks computed for the coupled model experiments (\textit{abrupt-4xCO$_2$}, \textit{1pctCO2} , and 
\textit{historical}) are shown in Table \ref{tab:lambda_AOGCM}.  The Earth's global mean energy budget is frequently used 
to compute sensitivities in the context of a forcing-response framework (e.g. Gregory et al., 2004; Andrews et al., 2015; 
Sherwood et al. 2015).  This is expressed as $N=F-R$ where the global heat uptake, or the radiative imbalance at the TOA 
($N; W\, m^{-2}$) is equal to the radiative forcing ($F;  W\, m^{-2}$) minus the radiative response, ($R; W\, m^{-2}$) which is 
often assumed to be $-\alpha T$, the product of the climate feedback parameter ($\alpha;  W\, m^{-2} K^{-1}$) and the change 
of the surface air temperature ($T; K$).  
Rather than using the linear regression method to calculate the ECS from the \textit{abrupt-4xCO$_2$} experiment, or calculating the 
traditional TCR value from the \textit{1pctCO2} experiment we use the differences in the global mean energy budget between control 
periods and the period of interest to calculate the climate feedback parameter as $-\alpha = (F-N)/T$. 
The advantage of this is that we can then use the same method to compute radiative feedback values from particular periods of the 
\textit{abrupt-4xCO$_2$}, \textit{1pctCO2} , \textit{historical} and \textit{amip} experiments.

@@

\textit{where should this paragraph go?}
The radiative feedbacks shown in Tables \ref{tab:lambda_AGCM} and \ref{tab:lambda_AOGCM} reveal a large range of 
net climate feedback parameter ($\alpha$; -0.46 to -2.13 $\rm{W m^{-2}K^{-1}}$) that results from differences in both the 
cloudy and clear sky fluxes.   
% The LW CLR feedback is nearly constant between the aquaplanet and various \textit{amip} experiments (LWCLR for abrupt??).   
% The SW CLR feedback is nearly constant across the \textit{amip} experiments but varies significantly
%between the \textit{aqua p4K} and the two coupled experiments (0.67 $\rm{W m^{-2}K^{-1}}$).
%The relatively large range of the SW CRE (from -0.65 $\rm{W m^{-2}K^{-1}}$ to 0.5 $\rm{W m^{-2}K^{-1}}$)
%confirms the important role played by mid- and low-level clouds outside of the region of 
%deep tropical convection where the LW and SW effects of clouds largely cancel.  
%
As described by Ringer et al., 2014, much of the range in the short wave clear-sky feedback can be attributed to differences 
in the experimental configurations of ice.  The aquaplanet experiments have no land and no sea ice.  
The \textit{amip} experiments have ice in the polar regions, but the ice is prescribed based on observations and 
only changes to a limited degree.  However, the fully coupled experiments \textit{abrupt-4xCO$_2$}, 
\textit{1pctCO2}, and \textit{historical} predict changes in the extent of sea-ice and show a larger positive SW CLR
feedback that results in part from the positive ice-albedo feedback.  
Thus, part of the range of values in the clear sky radiative fluxes is the result of differences in the physical configuration 
of the various experiments.  
However, the range of total feedback parameter among experiments that is due to differences in cloud feedbacks is not as easily connected to particular experimental configurations.

@@

\begin{figure}
  \centering
  %\includegraphics[width=\columnwidth]{cfmipfigs/Silvers_cfmip_CRE_SinglePanel_negativesign.pdf}
  \includegraphics[width=0.5\columnwidth]{cfmipfigs/Silvers_cfmip_CRE_3Pan_vert.pdf}
  \caption{The Cloud Radiative Effect (CRE) and CRE feedback of several CMIP6 experiments.  The top panel 
  shows (black) the CRE from two versions of the CERES-EBAF observations compared to 
  simulations of CRE using AM4.0 driven by the observed SST (\textit{amip}).  Also 
  shown in the top panel is the simulated CRE from three fully coupled CM4.0 experiments (\textit{historical} (yrs. 1950-2014),
  \textit{abrupt-4$\times$CO2} (yrs. 101-150), and \textit{1pctCO2} (yrs. 101-150)).  The middle panel shows an estimate of the 
  CRE feedback of the data in the top panels, computed by normalized according to the warming of surface air temperature over 
  the relevant time period.  The bottom panel shows the CRE feedback from four 
  CFMIP experiments (\textit{amip-p4K, amip-m4K, amip-future4K, aqua-p4K}).  The sign of the \textit{amip-m4K} experiment has 
  been reversed.}
  \label{fig:CRE_feedback}
\end{figure}

@@

%To compute the cloud feedback based on the CRE, the control state CRE of 
%the \textit{amip} and \textit{aqua} experiments is subtracted from the CRE in the perturbed experiment.  
To gain further insight into the sources of differences among the CRE values in Tables  \ref{tab:lambda_AGCM}  and  
\ref{tab:lambda_AOGCM}  we plot the observed CRE as a function of latitude alongside the CRE from the 
experiments shown in Table  \ref{tab:lambda_AOGCM}.  Observations from CERES-EBAF are shown for version 
2.8 (black dashed) and for version 4.1 (black).  During the development of AM4.0 version 2.8 of CERES-EBAF was 
used extensively \cite{Zhao_etal_2018a}.  The distributions of CRE in warming experiments are not directly comparable 
to observations from recent periods but rather show how potential changes in the effects of clouds vary with latitude.   
Note the large differences in the arctic and the shift poleward in the SH of the minimum in CRE.

The middle panel of Figure \ref{fig:CRE_feedback} shows the CRE feedback in the three coupled CM4.0 experiments and in the \textit{amip} experiment.  Values shown in Table \ref{tab:lambda_AOGCM} imply that the clouds present in the \textit{1pctCO$_2$} and \textit{abrupt4xCO$_2$} experiments
do not have as much of a cooling effect as they do in the \textit{historical} and \textit{amip} experiments.  The middle panel of Figure \ref{fig:CRE_feedback} illustrates that this is due to the warming experiments having a CRE feedback that is near zero or slightly positive throughout much of the mid-latitudes and tropics while the \textit{historical} experiment shows a negative CRE feedback at nearly all latitudes.  Comparing the \textit{amip} CRE feedback to the warming experiments in the 
middle panel of Figure \ref{fig:CRE_feedback} is more difficult due to the large positive CRE in the tropics and the very strong negative feedback between about 40-65$^{\circ}$S.  Anomalies in the middle panel of Figure \ref{fig:CRE_feedback} have been computed relative to the \textit{piControl} experiment.  The CRE and warming in Table \ref{tab:lambda_AOGCM} are 
computed for the years 1996-2014 (\textit{historical} and \textit{amip}) and years 100-150 (\textit{1pctCO$_2$} and \textit{abrupt4xCO$_2$}).

@@

@@

 \begin{table}
\begin{center}
\caption{Experiments used.   The years listed for each experiment correspond to the years specified by 
CMIP6, except for \textit{piControl}.  In most cases these are also the years used for analysis, but some 
figures use shorter time periods, see Figure captions for details.  }
    \begin{tabular}{*{4}{c}}
    \hline
    \hline
 Experiment & Class & Configuration & Years   \\ \hline
    \textit{historical}        &   DECK      &  atmosphere \& ocean   &  Jan 1850 -Dec 2014               \\ 
    \\
    \textit{abrupt-4xCO$_2$}   & DECK       &  atmosphere \& ocean       & 150 years  \\  
    \\
    \textit{1pctCO$_2$}   & DECK        &  atmosphere \& ocean  & 150 years \\  
    \\
    \textit{piControl}  & DECK   &  atmosphere \& ocean  &   years 250-350  \\  
    \\
    \textit{amip}  & DECK \& CFMIP   &  atmosphere   & Jan 1979 - Dec 2014  \\  
    \\
    \textit{amip-p4K}  & CFMIP       &  atmosphere   & Jan 1979 - Dec 2014  \\ 
    \textit{amip-m4K}   & CFMIP       &  atmosphere   & Jan 1979 - Dec 2014 \\ 
    \textit{amip-future4K}  & CFMIP  & atmosphere & Jan 1979 - Dec 2014 \\
    \textit{aqua-control}        & CFMIP  & atmosphere  & 10 years \\
    \textit{aqua-p4K}  & CFMIP    & atmosphere  &  10 years \\ \hline

>>>>

\subsection{Overall assessment of AM4 and CM4? Here or beginning of next section?}

\subsection{data and experiments}

@@

Before discussing the climate sensitivities of AM4/CM4 and how they are influenced by cloud feedbacks we assess
the clouds and radiative fluxes which are simulated by AM4.0 over the recent period of 1979-2014.  This is done 
by comparing satellite based observations to the \textit{amip} experiment that is part of GFDLs 
contribution to CMIP6.  
During the development and documentation of AM4.0 \cite{Zhao_etal_2018a, Zhao_etal_2018b}, 
(Z18a and Z18b hereafter) 
and CM4 \cite{Held_etal_2019}, specific cloud properties such as the 
cloud droplet number, cloud fraction, and the partition of cloud water into liquid or ice were noted, but 
accurately modeling the radiative fluxes at the top of the atmosphere was determined to be a 
higher priority partly because of the large observational uncertainties of those cloud properties (Z18a,b).   
Based on the initial analysis for those papers, the cloud properties of AM4.0 were determined to be
at least as consistent with observations as previous generations of GFDL models.  Z18a also noted 
that AM4.0 underestimates the liquid droplet number over oceans and downwind of the aerosol emission 
sources.    \textcolor{red}{Could be a good place to state phase related findings and results from Fan et al.}
Comparisons of AM4.0 with observations from ISCCP and MODIS in Z18a (their Figure 10) showed an underestimate of 
the optically thin low clouds and the mid-level clouds.  
However, the observational uncertainty for some of these properties prohibited firm conclusions.  This paper
uses additional observations and a more thorough analysis of the clouds in AM4/CM4 to better determine 
the quality of the cloud simulations.        
In this section we first compare the simulated and observed cloud fraction.  We then compare  
the simulated TOA radiative fluxes from AM4.0 to those observed by CERES.

@@

\textit{should this go in the section that is a general summary of AM4/CM4?}

@@

During the developmental of the AM4.0 GFDL model particular care was given to ensuring that the energy budget at 
the top of the atmosphere compared well with observations (Z18a).  The data set that was used as a target
was the CERES-EBAF TOA radiative fluxes, version 2.8 (Loeb et al., 2009).  
% probably don't need the next few sentences but here they are for now...
As a result of this focus AM4.0 succeeded at decreasing several long standing biases from previous GFDL models.  
In particular AM4.0 has a reduced tropical OLR bias and a reduced SW bias over much of the southern hemisphere oceans.   
Based on AM4.0 data that was used for the CMIP6 \textit{amip} experiment, the total TOA flux bias is -0.15 $ \rm{W m^{-2}}$,  % Fig 6 from Z18a
the bias in CRE due to longwave radiative fluxes is $-2.4 \rm{W m^{-2}} $ and the bias due to CRE of the shortwave radiative fluxes   
is $-1.1 \rm{W m^{-2}} $.  
% https://eosweb.larc.nasa.gov/project/ceres/ebaf_toa_table.    % webpage with CERES info
After the AM4.0 development was frozen and the process of documentation 
was underway, the CERES-EBAF data version 4.1 was released (Loeb et al., 2018).  When comparing the same 
AM4.0 \textit{amip} experiment to the 
newer version of CERES-EBAF data we find biases of $-2.2 \rm{W m^{-2}} $ for the longwave CRE and 
$-2.9 \rm{W m^{-2}} $ for the shortwave CRE (Figure \ref{fig:ceres_cre_4p1}).  Although the magnitude of bias 
differs when compared to the two versions of CERES-EBAF, the spatial pattern is very similar.   
The comparison of the total 
CRE in Figure \ref{fig:ceres_cre_4p1}  shows a cooling of about 25 $\rm{W m^{-2}}$ in AM4.0 which is about 
5 $\rm{W m^{-2}}$ more than CERES-EBAF.  The overall pattern compares
well with the observations although the cooling from the highly reflective stratocumulus regions is too small and
too far from the coastlines. 
This bias is clearly seen in the SW CRE and highlights the regions with the largest
positive CRE bias resulting from too few stratocumulus clouds.  Also of note is a pervasive negative bias in the SH oceans.   
  As previously discussed (e.g. Kay et al., 2012) these longwave and shortwave CRE 
biases are difficult to interpret because model developers often tune models to match particular CERES-EBAF data 
sets despite the well known fact that different versions of the CERES-EBAF data lead to changes in the observed CRE of
several $\rm{W m^{-2}}$.   Our aim in discussing this for AM4.0 is transparency in the model development process, 
as well as to point out that AM4.0 represents a significant improvement in the spatial biases over previous versions
of GFDL models (Z18a) and that both versions of the CERES-EBAF data show similar spatial patterns of bias in the 
simulated clouds  from the AM4.0 \textit{amip} experiment.

@@

The most recent generation of models developed at NOAA's GFDL that have participated in CMIP6 have a large range of climate 
sensitivities (possibly cite Winton et al., Dunne et al.) depending on the experiment of interest, the method used for 
calculation, and the particular model configuration.  One way of quantifying this sensitivity is with the climate feedback parameter, which, for the subset of GFDL models and CMIP6 experiments studied in this paper, varies between -0.46 and -2.1 $\rm{W m^{-2}K^{-1}}$ (Table 1).  
These models (AM4.0 Aquaplanet, AM4.0, CM4.0) simulate several 
distinct geophysical configurations which account for some of the range in values of the climate feedback parameter.  
However, our hypothesis is that the large range of climate sensitivities that are found within this 
group of models is in large part due to variations in the clouds (both their climatology and their feedbacks).

@@

It is also instructive to examine the values of the climate feedback parameters that result from experiments that include a 
dynamic ocean.  Feedbacks computed for the coupled model experiments (\textit{abrupt-4xCO$_2$}, \textit{1pctCO2} , and 
\textit{historical}) are shown in Table \ref{tab:lambda_AOGCM}.  The Earth's global mean energy budget is frequently used 
to compute sensitivities in the context of a forcing-response framework (e.g. Gregory et al., 2004; Andrews et al., 2015; 
Sherwood et al. 2015).  This is expressed as $N=F-R$ where the global heat uptake, or the radiative imbalance at the TOA 
($N; W\, m^{-2}$) is equal to the radiative forcing ($F;  W\, m^{-2}$) minus the radiative response, ($R; W\, m^{-2}$) which is 
often assumed to be $-\alpha T$, the product of the climate feedback parameter ($\alpha;  W\, m^{-2} K^{-1}$) and the change 
of the surface air temperature ($T; K$).  
Rather than using the linear regression method to calculate the ECS from the \textit{abrupt-4xCO$_2$} experiment (ECS of CM4.0 = 34543, Zelinka et al., 2019), or calculating the 
traditional TCR value from the \textit{1pctCO2} experiment (TCR of CM4.0 = 345, Winton et al., 2020) we use the differences in the global mean energy budget between control 
periods and the period of interest to calculate the climate feedback parameter as $-\alpha = (F-N)/T$. 
The advantage of this is that we can then use the same method to compute radiative feedback values from particular periods of the 
\textit{abrupt-4xCO$_2$}, \textit{1pctCO2} , \textit{historical} and \textit{amip} experiments.

@@

\textit{where should this paragraph go?}
The radiative feedbacks shown in Tables \ref{tab:lambda_AGCM} and \ref{tab:lambda_AOGCM} reveal a large range of 
net climate feedback parameter ($\alpha$; -0.46 to -2.13 $\rm{W m^{-2}K^{-1}}$) that results from differences in both the 
cloudy and clear sky fluxes.   
% The LW CLR feedback is nearly constant between the aquaplanet and various \textit{amip} experiments (LWCLR for abrupt??).   
% The SW CLR feedback is nearly constant across the \textit{amip} experiments but varies significantly
%between the \textit{aqua p4K} and the two coupled experiments (0.67 $\rm{W m^{-2}K^{-1}}$).
%The relatively large range of the SW CRE (from -0.65 $\rm{W m^{-2}K^{-1}}$ to 0.5 $\rm{W m^{-2}K^{-1}}$)
%confirms the important role played by mid- and low-level clouds outside of the region of 
%deep tropical convection where the LW and SW effects of clouds largely cancel.  
%
As described by Ringer et al., 2014, much of the range in the short wave clear-sky feedback can be attributed to differences 
in the experimental configurations of ice.  The aquaplanet experiments have no land and no sea ice.  
The \textit{amip} experiments have ice in the polar regions, but the ice is prescribed based on observations and 
only changes to a limited degree.  However, the fully coupled experiments \textit{abrupt-4xCO$_2$}, 
\textit{1pctCO2}, and \textit{historical} predict changes in the extent of sea-ice and show a larger positive SW CLR
feedback that results in part from the positive ice-albedo feedback.  
Thus, part of the range of values in the clear sky radiative fluxes is the result of differences in the physical configuration 
of the various experiments.  
However, the range of total feedback parameter among experiments that is due to differences in cloud feedbacks is not as easily connected to particular experimental configurations and requires further investigation.  One of the aims of this paper is to clarify the role that clouds play in 
these different feedback values.

@@

\begin{figure}
  \centering
  %\includegraphics[width=\columnwidth]{cfmipfigs/Silvers_cfmip_CRE_SinglePanel_negativesign.pdf}
  \includegraphics[width=0.5\columnwidth]{cfmipfigs/Silvers_cfmip_CRE_3Pan_vert.pdf}
  \caption{The observed and modeled Cloud Radiative Effect (CRE) and CRE feedback.  The top panel 
  shows the CRE from two versions of the CERES-EBAF observations (dashed black, version 2.8; solid black, version 4.1) as well as the CRE from four CMIP6 experiments.  These include one atmosphere only (\textit{amip}), and three fully coupled (\textit{historical} (yrs. 1950-2014), \textit{abrupt-4$\times$CO2} (yrs. 101-150), and \textit{1pctCO2} (yrs. 101-150)) experiments.  
  The middle panel shows an estimate of the CRE feedback of the experiments in the top panel, computed by normalizing according to the     
  warming of surface air temperature over the time period indicated in this caption, relative to the CMIP6 \textit{piControl} experiment.  
  The bottom panel shows the CRE feedback from four CFMIP experiments (\textit{amip-p4K, amip-m4K, amip-future4K, aqua-p4K}), computed relative to the \textit{amip} and \textit{aqua-Control} experiments.  The sign of the \textit{amip-m4K} experiment has been reversed.}
  \label{fig:CRE_feedback}
\end{figure}

@@

%To compute the cloud feedback based on the CRE, the control state CRE of 
%the \textit{amip} and \textit{aqua} experiments is subtracted from the CRE in the perturbed experiment.  
To gain further insight into the sources of differences among the CRE values in Tables  \ref{tab:lambda_AGCM}  and  
\ref{tab:lambda_AOGCM}  we plot (Figure \ref{fig:CRE_feedback}) the observed CRE as a function of latitude alongside the CRE from the 
experiments shown in Table  \ref{tab:lambda_AOGCM}.  Observations from CERES-EBAF are shown for version 
2.8 (black dashed) and for version 4.1 (black).  
%During the development of AM4.0 version 2.8 of CERES-EBAF was used extensively \cite{Zhao_etal_2018a}.  
While the distributions of CRE in warming experiments are not directly comparable to observations from recent periods, they provide context for how potential changes in the effects of clouds could vary with latitude.   
Note the large differences in the arctic and the shift poleward in the SH of the minimum in CRE.

The middle panel of Figure \ref{fig:CRE_feedback} shows the CRE feedback from three coupled CM4.0 experiments and the \textit{amip} experiment.  Values shown in Table \ref{tab:lambda_AOGCM} imply that the clouds present in the \textit{1pctCO$_2$} and \textit{abrupt4xCO$_2$} experiments
do not have as much of a cooling effect as they do in the \textit{historical} and \textit{amip} experiments.  The middle panel of Figure \ref{fig:CRE_feedback} illustrates that this is due to the warming experiments having a CRE feedback that is near zero or slightly positive throughout much of the mid-latitudes and tropics while the \textit{historical} experiment shows a negative CRE feedback at nearly all latitudes.  Comparing the \textit{amip} CRE feedback to the warming experiments in the 
middle panel of Figure \ref{fig:CRE_feedback} is more difficult due to the large positive CRE in the tropics and the very strong negative feedback between about 40-65$^{\circ}$S.  Anomalies in the middle panel of Figure \ref{fig:CRE_feedback} have been computed relative to the \textit{piControl} experiment.  The CRE and warming in Table \ref{tab:lambda_AOGCM} are 
computed for the years 1996-2014 (\textit{historical} and \textit{amip}) and years 100-150 (\textit{1pctCO$_2$} and \textit{abrupt4xCO$_2$}).

@@

While potentially confusing, we show cloud fraction anomalies computed relative to two different control experiments, \textit{piControl} and \textit{amip}.  This is important because the cloud feedback values are usually computed relative to these control experiments and we find it instructive to see how the control experiment used can influence the cloud anomalies which are found.  First, there are many similarities in the cloud anomalies regardless of the control used (e.g. Increased upper-level deep tropical and polar clouds, decreased mid-level mid-latitude clouds, and in some cases, decreases of low-level tropical clouds).  Where the anomalies differ substantively is between the low-level clouds in the high-latitude regions.  If we take the \textit{amip} experiment to be the one that is closest to the observations, then the bottom center panel shows a different of about 8\% in the cloud fraction between the \textit{amip} and \textit{piControl} experiments between $60-80^\circ$.  Is this an artifact of sea ice being prescribed in \textit{amip}??  It seems that the large diffference between the low-level clouds of this region in the amip-like and coupled experiments indicates either a sensitivity to the configuration (sea-ice differences), or the result of SST biases that are created by the coupled models.

The bottom right panel shows very clearly the different responses of clouds to the amip-p4K and amip-future4K experiments.  The low-level cloud fraction of the amip-p4K and amip-future4K are nearly identical in the NH but are not even the same sign in the SH.

@@

 \begin{table}
\begin{center}
\caption{Experiments used.   The years listed for each experiment correspond to the years specified by 
CMIP6, except for \textit{piControl}.  In most cases these are also the years used for analysis, but some 
figures use shorter time periods, see Figure captions for details.  }
    \begin{tabular}{*{5}{c}}
    \hline
    \hline
 Experiment & Class & Configuration & Years  &   Data doi  \\ \hline
    \textit{historical}        &   DECK      &  CM4.0: AOGCM   &  Jan 1850 -Dec 2014               \\ 
    \\
    \textit{abrupt-4xCO$_2$}   & DECK       &  CM4.0: AOGCM       & 150 years  \\  
    \\
    \textit{1pctCO$_2$}   & DECK        &  CM4.0: AOGCM  & 150 years \\  
    \\
    \textit{piControl}  & DECK   &  CM4.0: AOGCM  &   years 250-350  \\  
    \\
    \textit{amip}  & DECK/CFMIP   &  AM4.0: AGCM   & Jan 1979 - Dec 2014  \\  
    \\
    \textit{amip-p4K}  & CFMIP       &  AM4.0: AGCM   & Jan 1979 - Dec 2014  & 10.22033/ESGF/CMIP6.8508  \\ 
    \textit{amip-m4K}   & CFMIP       &  AM4.0: AGCM   & Jan 1979 - Dec 2014 \\ 
    \textit{amip-future4K}  & CFMIP  & AM4.0: AGCM & Jan 1979 - Dec 2014 \\
    \textit{aqua-control}        & CFMIP  & AM4.0: Aqua  & 10 years \\
    \textit{aqua-p4K}  & CFMIP    & AM4.0: Aqua &  10 years \\ \hline
